Naturalness in U(1) extensions of the MSSM

### 2015-01-16 paper/e6ssm-tuning-paper.tex
Fixed some typos that were stopping the pdf from compiling, but otherwise left the text unchanged, and added cutoff scan plots to the repository

The complicated shape of the E6SSM fine tuning curve can be understood
by looking at the indivual sensitivities shown in bottom left panel.
In this case one can see that the tuning is initially dominated by the
$\Delta_\lambda$ sensitivity, which contains some terms proprtional to
$M_Z^{\prime \, 2}$.  As the cutoff scale is raised however fine
tuning contributions from the stops and gluino start to feed into the
sensitivities, in particular $\Delta_{m_{H_u}^}2$ and $\Delta_\lamda$.
In the latter these contribution have the opposite sign to those from
$M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
passes through zero.  However in $\Delta_{m_{H_u}^}2$ dominating at
larger values of the cutoff scale we see the effect of the more common
fine tuning problem where the stops add large contributions to
$m_{H_u}^2$ , in this case leading to a large cancellation between
$m_{H_u}^2(M_X)$ and $m_{Q_3}^2(M_X)$ inside $m_{H_u}^2(M_{SUSY})$.

@@

In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV. This is diue to ? large A_t mixing?, $M_3$? different RGEs?

>>>>

The complicated shape of the E6SSM fine tuning curve can be understood
by looking at the indivual sensitivities shown in bottom left panel.
In this case one can see that the tuning is initially dominated by the
$\Delta_\lambda$ sensitivity, which contains some terms proprtional to
$M_Z^{\prime \, 2}$.  As the cutoff scale is raised however fine
tuning contributions from the stops and gluino start to feed into the
sensitivities, in particular $\Delta_{m_{H_u}^2}$ and $\Delta_\lambda$.
In the latter these contribution have the opposite sign to those from
$M_Z^\prime$ leading to this strange behaviour where $\Delta_\lambda$
passes through zero.  However in $\Delta_{m_{H_u}^2}$ dominating at
larger values of the cutoff scale we see the effect of the more common
fine tuning problem where the stops add large contributions to
$m_{H_u}^2$ , in this case leading to a large cancellation between
$m_{H_u}^2(M_X)$ and $m_{Q_3}^2(M_X)$ inside $m_{H_u}^2(M_{SUSY})$.

@@

In this particular case the fine tuning of the E$_6$SSM benchmark becomes larger than that od the MSSM benchmark when $M_X\approx 10^{10}-10^{11}$ GeV. This is diue to ? large $A_t$ mixing?, $M_3$? different RGEs?
